Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-12-15 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{deluxetable}{|cccccc|rr|rr|}
    \tablecaption{Prevalence of involvement patterns in the multi-centric dataset. An involvement pattern is characterized by the state of the six \glspl{lnl}: A red dot means the \gls{lnl} was reported to be metastatic, a green dot means it was determined to be healthy and a question mark means that the prevalence was marginalized over the state of this \gls{lnl}. \label{table:data_prevalence}}
    \tablehead{
        \multicolumn{6}{|c|}{\textbf{LNL involvement} } & \multicolumn{4}{c|}{\textbf{T-category} } \\
        I & II & III & IV & V & VII & \multicolumn{2}{c}{\textbf{early} } & \multicolumn{2}{c|}{\textbf{late} } \\
    }
    \startdata
    \variable{output/data_table.tex}
    \enddata
\end{deluxetable}

>>>>

\begin{deluxetable}{ccccccrrrr}
    \tablecaption{Prevalence of involvement patterns in the multi-centric dataset. An involvement pattern is characterized by the state of the six \glspl{lnl}: A red dot means the \gls{lnl} was reported to be metastatic, a green dot means it was determined to be healthy and a question mark means that the prevalence was marginalized over the state of this \gls{lnl}. \label{table:data_prevalence}}
    \tablehead{
        \multicolumn{6}{c}{\textbf{LNL involvement} } & \multicolumn{4}{c}{\textbf{T-category} } \\
        I & II & III & IV & V & VII & \multicolumn{2}{c}{\textbf{early} } & \multicolumn{2}{c}{\textbf{advanced} }
    }
    \startdata
    \variable{output/data_table.tex}
    \enddata
\end{deluxetable}
